Theory about Normal Basis on $F(2^k)$

### 2017-03-03 dissertation/submission/conclude.tex
dissertation: after submission_1st revision
after submission: revision 2

Our approaches still have limitations: for word-level FSM traversal and 
sequential GF multiplier verification, our methods are more efficient
for XOR-rich circuits, while most industrial designs are AND-OR gate dominant.
For UNSAT core extraction, the abstraction refinement approach such as $k$-BMC 
has only limited application on certain model checking problems. To overcome these limitations,
the following further explorations are worthy of investigation.

\section{Future Work}
In this section, we highlight some research problems that deserve further study.
\subsection{Multivariate Polynomial Ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote the
next state. However, in some situations we need to keep recording the relations between $T$ and
the inputs, {\it e.g.} the reached states contain multivariate polynomials in $T$, as well as 
PS variable $S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multivariate polynomials,
the set complement requires an extension of Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We conjecture as follows:

@@

\IncMargin{1em}
\begin{algorithm}[hbt]
\SetAlgoNoLine
\LinesNumbered
 \KwIn{Transition polynomial $f_t = T + \mathcal F (S,x)$, 
	initial state ideal $from^0 = \langle S+\mathcal G(x), x^{q_1} - x\rangle$}
 \KwOut{Reachable states}
  $reached = from^0(T\setminus S)$\;
  \Repeat{$GB(new^i) == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB$(\langle f_t, from^{i-1}\rangle) \setminus \mathcal H(S)$\;
	$\overline{reached} = \langle T^{q_2}-T, x^{q_1} - x \rangle : reached$\;
	$new^i \gets $GB$(to^i + \overline{reached})$\;
  	$reached \gets $GB$( reached \cdot new^i)$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm (multivariate-generator ideals)}\label{alg:multi}
\end{algorithm}
\DecMargin{1em}

The inputs of this algorithm includes the transition polynomial (result of word-level abstraction) and initial 
states description ideal, which contains 2 generators corresponding to constraints of PI and combinational input $S$. 
For example, $\langle S+1+\alpha, x^2+x\rangle$ means initial state$=\{11\}$,
$\langle S+x\cdot\alpha, x^2+x\rangle$ means initial states$=\{00,10\}$).

@@

Considering the Buchberger's algorithm, all generators' leading terms are relatively prime, so $I_{tran}$ is a GB itself. 
Furthermore, generator $S + \mathcal G(x)$ could (possibly) be reduced by $v_x$,
and $T+\mathcal F(S,x)$ will definitely reduced by $S + \mathcal G(x)$. In the end we obtain a polynomial
$T + \mathcal F'(x)$ in the reduced GB. We can then include this polynomial and $v_x$ and exclude the polynomial containing
$S$ ({\it i.e.} $\mathcal H(S)$ in Algorithm \ref{alg:multi}), to compose an ideal representing \emph{next states} $to^i$. 
In iteration 1, the result is $to^1 = \langle T+1, x^2+x\rangle$

Line 5 is the ideal quotient of universal set and reached states. In the first iteration, 
$reached$ is the initial state $\langle T+1+\alpha, x^2+x \rangle$. Result of ideal quotient
is $\langle T^3+(1+\alpha)T^2+\alpha T, x^2+x\rangle$ represents $\{00,01,10\}$.

Line 6 is ideals' sum (intersection of their varieties), it is done by combining all generators
from 2 ideals and compute GB. In the first iteration, the result is $GB(\langle T+1,T^3+(1+\alpha)T^2+\alpha T, x^2+x\rangle) = \langle T+1, x^2+x\rangle$ representing $\{01\}$.

Line 7 is ideals' product (union of their varieties), it is done by multiplying all pairs of
generators from both ideal. For the first iteration it gives the result as $GB(\langle (T+1)(T+1+\alpha),
(T+1)(x^2+x), (T+1+\alpha)(x^2+x), (x^4+x)\rangle) = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$ representing $\{01,11\}$.

The traversal algorithm executes 3 iterations and terminate at 4th iteration. We list all intermediate 
results below:
\begin{itemize}
\item Iteration 1: $from^0 = \langle S+1+\alpha, x^2+x\rangle, to^1 = \langle T+1, x^2+x\rangle,
 reached = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$
\item Iteration 2: $from^1 = \langle S+1, x^2+x\rangle, to^2= \langle T+\alpha, x^2+x\rangle,
reached = \langle T^3+1, x^2+x\rangle$
\item Iteration 3: $from^2 = \langle S+\alpha, x^2+x\rangle, to^3 = \langle T+\alpha x, x^2+x
\rangle, reached = \langle T^3\cdot x+x, T^4+T, x^2+x\rangle$
\item Iteration 4: $from^3 = \langle S, x\rangle, to^4 = \langle T+1, x\rangle, new = \langle1\rangle$
\end{itemize}
The final reachable states are represented by a multivariate polynomial ideal $\langle T^3\cdot x+x, T^4+T, x^2+x\rangle$,
which denotes $\{00,01,10,11\}$.
\end{Example}

\subsection{Use of the $F_4$ Algorithm and ZDDs to Accelerate GB Reduction}
In Chapters \ref{ch:reacha} and \ref{ch:normal}, by using RATO we transform the GB-based
computation to that of a multivariate polynomial division. However, this division (reduction)
still incurs exponential complexity in the worst case. In a situation where division is to be performed modulo
a chain of OR gates, the size of remainder polynomial will explode. For example, a chain of OR gates 
can be written as the Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
which equals to the following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice, $f$ contains $2^4-1 = 15$ terms, which is exponential in the number of variables.
The size explosion is a major factor affecting the efficiency of polynomial division.

@@

Another way is to utilize DDs, {\it e.g.} ZDDs. ZDDs can represent unate covers of Boolean formulas.
We can represent $f$ using a ZDD, where every path in the ZDD from a root to a terminal corresponds
to a monomial term.

\begin{figure}[h]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/ZDD.eps}
}
\caption{A ZDD representing remainder polynomial reducing by a chain of OR gates with order $d>c>b>a$.}
\label{fig:ZDD}
\end{figure}

@@

\subsection{Craig Interpolants in Algebraic Geometry}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulae
\cite{pudlak:ci} \cite{mcmillan2003interpolation}. Assume that Boolean
formulae are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

@@

CIs are used to derive abstractions to produce over-approximate image
operators in model checking \cite{mcmillan2003interpolation}. Since $A
\implies P$, $P$ contains $A$ and is an {\it abstraction} of $A$. It
also has fewer variables, so checking  invariants on $P \wedge B$ is
easier. The interpolant is derived through a resolution proof of the
SAT problem. There can be many interpolants $P_i$ for a pair $(A,B)$; 
however, it is not feasible to explore a few or all of these
interpolants by means of the resolution proof.

@@

Existence of algebraic interpolant comes from \cite{craig-interpolate}.
The question for exploring is that how do we compute it in algebraic geometry?

@@

As there can be many interpolants for an ideal-pair $(J_A, J_B)$, 
the following questions should also be investigated in the future:
\bi
\item Find the minimal interpolant: {\it i.e.} find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the remaining
  variables. Consider Figure \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: projection of varieties on common variables.}
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-Level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional/macro blocks (including IP cores) and a raw netlist.
Technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as a alternative way to perform technology mapping, especially on word-level when 
given blocks represent word-level functions.

@@

\begin{Problem}
Given a gate-level design $N$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $N$, and write out the mapped design $N'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $N'$ with as many of $B_i$ such that the area
and timing is optimal. The procedure is also illustrated in Figure \ref{fig:macro}.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/macro.pdf}
	\end{center}
	\caption{The outline and flow of technology mapping of macro blocks.}
	\label{fig:macro}
\end{figure}

@@

The following part describes the sketch of our proposed approach base on loop invariant constraints \cite{sankaranarayanan2004non}.
First, a transition system is modeled by algebraic assertions; then \emph{ideal membership test} \cite{lv:phd}
is applied on the set of assertions to help abstract the loop invariant. We introduce concept \emph{template}
from \cite{sankaranarayanan2004non} to apply on our proposed approach.

1) {\bf Template and state constraints:}  Ideal membership test requires a setup of ideal $J_{loop}$
for loop invariants. 
One heuristic that can provide better coverage for loop invariant abstraction as well as a
relatively small size is \emph{generic quadratic form} (GQF).

@@

In the next step, we reduce the template with the Gr\"obner basis $G$: $\Func \xrightarrow{G}_+ r$, the remainder equals to
$$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$$
Let it equal to 0, then each coefficient will generate a constraint. The solution to the system forms the candidate
assignment to generate loop invariants.
\begin{equation}
\label{eqn:parasys}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\end{equation}

3) {\bf Modeling state transitions:}
A typical state transition starts from the previous state (PS) and ends at next state (NS). 
Our proposed approach models the 2 states individually,
{\it i.e.} performs polynomial reduction separately and obtains remainder $r_1$ and $r_2$. 
Assume a constraint polynomial describing
the state transition is $r_t$, then we require that when invariant of PS holds and transition $PS \to NS$ stands,
the invariant of NS should also be satisfied:
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ can be any polynomial in arbitrary rings. To make it practical, in terms of solving the system, 
we limit $\lambda$ to the polynomial ring with only real numbers.

Take Equation \ref{eqn:loopinv} as the example (which refers to Example 10 in \cite{sankaranarayanan2004non}). 
PS is initial state we just characterized 
$$\Func = f(s,i,j,j_0)$$ 
and NS has exactly the same form of constraint:
$$\Func' = f(s',i',j',j_0')$$
Considering the transition relation, we substitute $s'$ with $s+i$ and replace $j'$
with $j-1$, $i'$ for $i$, $j_0'$ for $j_0$, respectively. 
The template for NS is polynomial $f'$ in Example 10 in \cite{sankaranarayanan2004non}.

We then perform reduction with the Gr\"obner basis generated from the transition relation modeling, 
which is the Gr\"obner basis of polynomial ideal corresponding to the gates in the circuit partition.
After recording the NS remainder $r_2$,
by using equality $r_2 = \lambda r_1$ we get constraints for the parameters. We solve the system using 
similar algorithm to solve binate covering problems
which is also described in Section 4 as \emph{elimination by splitting} technique in \cite{sankaranarayanan2004non}. 
One of the branching results is:
\begin{align*}
&a_0,a_2,\dots, a_6, a_9,\dots,a_{14}=  0\\ 
&a_1=a_7=-a_8
\end{align*}
The reduced remainder is: 
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Thus the invariant of the program in Equation \ref{eqn:loopinv} is:
$$s = i(j_0- j)$$
We can verify the invariant by executing the program which calculates $i\times j_0$. 
Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Equation \ref{eqn:loopinv}.

@@

1) {\bf System abstraction:}
The polynomial we use to test ideal membership should include all the information of a circuit partition,
which requires us to abstract information from the system and write it into a single polynomial.
Usually this polynomial has the following generic form:
$$Z + f(i_1,i_2,\dots,i_n)$$
where $Z$ is the output. When there is only one output, $Z$ collapses to a bit-level variable. However in most
cases there are multiple outputs on the cut, indicating $Z$ as a word-level variable. Boolean function $\Func$ covers
all inputs, and $i_1,i_2,\dots,i_n$ are all bit-level inputs.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/tobemapped.pdf}
	\end{center}
	\caption{An example gate-level netlist of a target sub-circuit to be mapped. ``$\blacksquare$" denotes a pin, 
	which is the boundary for the mapper.}
	\label{fig:tobemapped}
\end{figure}

@@

After imposing ATO of LEX with
$$\textit{Other\ circuit\ variables} > \textit{output\ word\ } Z > \textit{all\ cut-set\ bit\ level\ inputs}$$
on the ideal describing the partitioned circuit as well as ideal with vanishing polynomials,
the reduced Gr\"obner basis has a single polynomial generator in the form of $Z + \Func(s_0,s_1,s_2,s_3)$.
In this example:

@@

2) {\bf Templates on Boundary Information:}
\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/template.pdf}
	\end{center}
	\caption{Candidate cell: a standard 2-bit adder with one possible input/output mapping.}
	\label{fig:template}
\end{figure}

Figure \ref{fig:template} shows a 2-bit standard cell. It has 3 outputs ($t_0,t_1,CO$) mapped to 2 output pins ($z_0,z_1$),
and 4 inputs ($a_0,a_1,b_0,b_1$) mapped to 3 input pins ($s_0,s_1,s_2$, the excessive input {\it e.g.} $b_1$ is assigned to fixed 0/1 signal). Dashed connection
lines show one possible mapping, to find out this kind of feasible mapping, we need to simulate
all possible mappings, where the concept "template" can be used.

@@

Above polynomial includes all possibilities where $z_0$ could be mapped to.
When $c_{n_0} = 0$, then $\{c_{t_0z_0},c_{t_1z_0},c_{z_0CO}\}$ equals to 1 denotes a valid mapping to corresponding output pin. 
Conversely if $c_{n_0} = 1$, the ``1" evaluation denotes mapping to negation of corresponding output pin.

@@

\item Second, propagate forward the cut for a certain number of gates (depth), choose a cut-set
which fully dependents on these inputs as output pins. Thus we obtain a sub-circuit by partitioning;

\item Third, abstract a description polynomial $\Func$ of the target sub-circuit using GB based abstraction;

>>>>

Our approaches still have limitations: For word-level FSM traversal and 
sequential GF multiplier verification, our methods are more efficient
for XOR-rich circuits, while most industrial designs are AND-OR gate dominant.
For UNSAT core extraction, the abstraction refinement approach such as $k$-BMC 
has only limited application on certain model checking problems. To overcome these limitations,
the following further explorations are worthy of investigation.

\section{Future Work}
In this section, we highlight some research problems that deserve further study.
\subsection{Multivariate Polynomial Ideal Based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote the
next state. However, in some situations we need to keep recording the relations between $T$ and
the inputs, {\it e.g.} the reached states contain multivariate polynomials in $T$, as well as 
PS variable $S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multivariate polynomials,
the set complement requires an extension of Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We conjecture as follows:

@@

% \IncMargin{1em}
\begin{algorithm}[hbt]
\SetAlgoNoLine
\LinesNumbered
 \KwIn{Transition polynomial $f_t = T + \mathcal F (S,x)$, 
	initial state ideal $from^0 = \langle S+\mathcal G(x), x^{q_1} - x\rangle$}
 \KwOut{Reachable states}
  $reached = from^0(T\setminus S)$\;
  \Repeat{$GB(new^i) == 1$}
  {
  	$i \gets i + 1$\;
	$to^i \gets$GB$(\langle f_t, from^{i-1}\rangle) \setminus \mathcal H(S)$\;
	$\overline{reached} = \langle T^{q_2}-T, x^{q_1} - x \rangle : reached$\;
	$new^i \gets $GB$(to^i + \overline{reached})$\;
  	$reached \gets $GB$( reached \cdot new^i)$\;
	$from^i \gets new^i(S\setminus T)$\;
  }
\Return{$reached$}
\caption {Algebraic Geometry based Traversal Algorithm (multivariate-generator ideals)}\label{alg:multi}
\end{algorithm}
% \DecMargin{1em}

The inputs of this algorithm include the transition polynomial (result of word-level abstraction) and initial 
states description ideal, which contains 2 generators corresponding to constraints of PI and combinational input $S$. 
For example, $\langle S+1+\alpha, x^2+x\rangle$ means initial state$=\{11\}$,
$\langle S+x\cdot\alpha, x^2+x\rangle$ means initial states$=\{00,10\}$).

@@

Considering Buchberger's algorithm, all generators' leading terms are relatively prime, so $I_{tran}$ is a GB itself. 
Furthermore, generator $S + \mathcal G(x)$ could (possibly) be reduced by $v_x$,
and $T+\mathcal F(S,x)$ will definitely be reduced by $S + \mathcal G(x)$. In the end we obtain a polynomial
$T + \mathcal F'(x)$ in the reduced GB. We can then include this polynomial and $v_x$ and exclude the polynomial containing
$S$ ({\it i.e.}, $\mathcal H(S)$ in Algorithm \ref{alg:multi}), to compose an ideal representing \emph{next states} $to^i$. 
In iteration 1, the result is $to^1 = \langle T+1, x^2+x\rangle$

Line 5 is the ideal quotient of universal set and reached states. In the first iteration, 
The initial state $reached$ is $\langle T+1+\alpha, x^2+x \rangle$. The result of ideal quotient
is $\langle T^3+(1+\alpha)T^2+\alpha T, x^2+x\rangle$ represents $\{00,01,10\}$.

Line 6 is ideals' sum (intersection of their varieties) and is done by combining all generators
from 2 ideals and computing GB. In the first iteration, the result is $GB(\langle T+1,T^3+(1+\alpha)T^2+\alpha T, x^2+x\rangle) = \langle T+1, x^2+x\rangle$,
representing $\{01\}$.

Line 7 is ideals' product (union of their varieties) and is done by multiplying all pairs of
generators from both ideals. For the first iteration it gives the result as $GB(\langle (T+1)(T+1+\alpha),
(T+1)(x^2+x), (T+1+\alpha)(x^2+x), (x^4+x)\rangle) = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$, representing $\{01,11\}$.

The traversal algorithm executes 3 iterations and terminates at the 4th iteration. We list all intermediate 
results below:
\begin{itemize}
\item Iteration 1: $from^0 = \langle S+1+\alpha, x^2+x\rangle, to^1 = \langle T+1, x^2+x\rangle,
 reached = \langle T^2+\alpha T+(1+\alpha), x^2+x\rangle$
\item Iteration 2: $from^1 = \langle S+1, x^2+x\rangle, to^2= \langle T+\alpha, x^2+x\rangle,
reached = \langle T^3+1, x^2+x\rangle$
\item Iteration 3: $from^2 = \langle S+\alpha, x^2+x\rangle, to^3 = \langle T+\alpha x, x^2+x
\rangle, reached = \langle T^3\cdot x+x, T^4+T, x^2+x\rangle$
\item Iteration 4: $from^3 = \langle S, x\rangle, to^4 = \langle T+1, x\rangle, new = \langle1\rangle$
\end{itemize}
The final reachable states are represented by a multivariate polynomial ideal $\langle T^3\cdot x+x, T^4+T, x^2+x\rangle$,
which denotes $\{00,01,10,11\}$.
\end{Example}

\subsection{Use of the $F_4$ Algorithm and ZDDs to Accelerate GB Reduction}
In Chapters \ref{ch:reacha} and \ref{ch:normal}, by using RATO we transform the GB-based
computation to that of a multivariate polynomial division. However, this division (reduction)
still incurs exponential complexity in the worst case. In a situation where division is to be performed modulo
a chain of OR gates, the size of the remainder polynomial will explode. For example, a chain of OR gates 
can be written as the Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
which equals the following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice, $f$ contains $2^4-1 = 15$ terms, which is exponential in the number of variables.
The size explosion is a major factor affecting the efficiency of polynomial division.

@@

Another way is to utilize DDs, e.g., ZDDs. ZDDs can represent unate covers of Boolean formulas.
We can represent $f$ using a ZDD, where every path in the ZDD from a root to a terminal corresponds
to a monomial term.

@@

\begin{figure}[bp]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/ZDD.eps}
}
\caption{A ZDD representing remainder polynomial reducing by a chain of OR gates with order $d>c>b>a$.}
\label{fig:ZDD}
\end{figure}

\subsection{Craig Interpolants in Algebraic Geometry}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulas
\cite{pudlak:ci, mcmillan2003interpolation}. Assume that Boolean
formulas are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

@@

CIs are used to derive abstractions to produce overapproximate image
operators in model checking \cite{mcmillan2003interpolation}. Since $A
\implies P$, $P$ contains $A$ and is an {\it abstraction} of $A$. It
also has fewer variables, so checking  invariants on $P \wedge B$ is
easier. The interpolant is derived through a resolution proof of the
SAT problem. There can be many interpolants $P_i$ for a pair $(A,B)$; 
however, it is not feasible to explore a few or all of these
interpolants by means of the resolution proof.

@@

Existence of algebraic interpolant comes from \cite{craig-interpolate}.
The question for exploring is, how do we compute it in algebraic geometry?

@@

As there can be many interpolants for an ideal-pair $(J_A, J_B)$, 
the following questions should also be investigated in the future:
\bi
\item Find the minimal interpolant, i.e., find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the remaining
  variables. Consider Figure \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

\begin{figure}[bp]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: projection of varieties on common variables.}
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-Level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional/macro blocks (including IP cores) and a raw netlist.
Technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as an alternative way to perform technology mapping, especially at word level when 
given blocks represent word-level functions.

@@

\begin{Problem}
Given a gate-level design $N$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $N$, and write out the mapped design $N'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $N'$ with as many of $B_i$ such that the area
and timing are optimal. The procedure is also illustrated in Figure \ref{fig:macro}.

\begin{figure}[bp]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/macro.pdf}
	\end{center}
	\caption{The outline and flow of technology mapping of macro blocks.}
	\label{fig:macro}
\end{figure}

@@

The following part describes the sketch of our proposed approach based on loop-invariant constraints \cite{sankaranarayanan2004non}.
First, a transition system is modeled by algebraic assertions, then the \emph{ideal membership test} \cite{lv:phd}
is applied on the set of assertions to help abstract the loop invariant. We introduce concept \emph{template}
from \cite{sankaranarayanan2004non} to apply on our proposed approach.

1) {\bf Template and state constraints:}  The ideal membership test requires a setup of ideal $J_{loop}$
for loop invariants. 
One heuristic that can provide better coverage for loop-invariant abstraction as well as a
relatively small size is \emph{generic quadratic form} (GQF).

@@

In the next step, we reduce the template with the Gr\"obner basis $G$: $\Func \xrightarrow{G}_+ r$. The remainder equals to
$$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$$
Let it equal 0, then each coefficient will generate a constraint. The solution to the system forms the candidate
assignment to generate loop invariants.
\begin{equation}
\label{eqn:parasys}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\end{equation}

3) {\bf Modeling state transitions:}
A typical state transition starts from the previous state (PS) and ends at next state (NS). 
Our proposed approach models the 2 states individually,
i.e., performs polynomial reduction separately and obtains remainders $r_1$ and $r_2$. 
Assume a constraint polynomial describing
the state transition is $r_t$, then we require that when invariant of PS holds and transition $PS \to NS$ stands,
the invariant of NS should also be satisfied:
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ can be any polynomial in arbitrary rings. To make it practical, in terms of solving the system, 
we limit $\lambda$ to the polynomial ring with only real numbers.

Take Equation \ref{eqn:loopinv} as the example (which refers to Example 10 in \cite{sankaranarayanan2004non}). 
PS is the initial state we just characterized 
$$\Func = f(s,i,j,j_0)$$ 
and NS has exactly the same form of constraint:
$$\Func' = f(s',i',j',j_0')$$
Considering the transition relation, we substitute $s'$ with $s+i$ and replace $j'$
with $j-1$, $i'$ for $i$, $j_0'$ for $j_0$, respectively. 
The template for NS is polynomial $f'$ in Example 10 in \cite{sankaranarayanan2004non}.

We then perform reduction with the Gr\"obner basis generated from the transition relation modeling, 
which is the Gr\"obner basis of polynomial ideal corresponding to the gates in the circuit partition.
After recording the NS remainder $r_2$,
by using equality $r_2 = \lambda r_1$ we get constraints for the parameters. We solve the system using 
similar algorithm to solve binate-covering problems,
which is also described in Section 4 as \emph{elimination by splitting} technique in \cite{sankaranarayanan2004non}. 
One of the branching results is
\begin{align*}
&a_0,a_2,\dots, a_6, a_9,\dots,a_{14}=  0\\ 
&a_1=a_7=-a_8
\end{align*}
The reduced remainder is
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Thus the invariant of the program in Equation \ref{eqn:loopinv} is
$$s = i(j_0- j)$$
We can verify the invariant by executing the program which calculates $i\times j_0$. 
Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Equation \ref{eqn:loopinv}.

@@

1) {\bf System abstraction:}
The polynomial we use to test ideal membership should include all the information of a circuit partition,
which requires us to abstract information from the system and write it into a single polynomial.
Usually this polynomial has the following generic form:
$$Z + f(i_1,i_2,\dots,i_n)$$
where $Z$ is the output. When there is only one output, $Z$ collapses to a bit-level variable. However, in most
cases there are multiple outputs on the cut, indicating $Z$ as a word-level variable. Boolean function $\Func$ covers
all inputs, and $i_1,i_2,\dots,i_n$ are all bit-level inputs.

\begin{figure}[tbp]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/tobemapped.pdf}
	\end{center}
	\caption{An example gate-level netlist of a target sub-circuit to be mapped. ``$\blacksquare$" denotes a pin, 
	which is the boundary for the mapper.}
	\label{fig:tobemapped}
\end{figure}

@@

After imposing ATO of LEX with
$$\textit{Other\ circuit\ variables} > \textit{output\ word\ } Z > \textit{all\ cut-set\ bit\ level\ inputs}$$
on the ideal describing the partitioned circuit as well as the ideal with vanishing polynomials,
the reduced Gr\"obner basis has a single polynomial generator in the form of $Z + \Func(s_0,s_1,s_2,s_3)$.
In this example:

@@

2) {\bf Templates on Boundary Information:}
\begin{figure}[bp]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/template.pdf}
	\end{center}
	\caption{Candidate cell: a standard 2-bit adder with one possible input/output mapping.}
	\label{fig:template}
\end{figure}

Figure \ref{fig:template} shows a 2-bit standard cell. It has 3 outputs ($t_0,t_1,CO$) mapped to 2 output pins ($z_0,z_1$),
and 4 inputs ($a_0,a_1,b_0,b_1$) mapped to 3 input pins ($s_0,s_1,s_2$, the excessive input {\it e.g.} $b_1$ is assigned to fixed 0/1 signal). Dashed connection
lines show one possible mapping, to find out this kind of feasible mapping, we need to simulate
all possible mappings where the concept "template" can be used.

@@

The above polynomial includes all possibilities where $z_0$ could be mapped to.
When $c_{n_0} = 0$, then $\{c_{t_0z_0},c_{t_1z_0},c_{z_0CO}\}$ equals 1 denotes a valid mapping to a corresponding output pin. 
Conversely if $c_{n_0} = 1$, the ``1" evaluation denotes mapping to negation of corresponding output pin.

@@

\item Second, propagate forward the cut for a certain number of gates (depth), choose a cut-set
which fully depends on these inputs as output pins. Thus we obtain a subcircuit by partitioning;

\item Third, abstract a description polynomial $\Func$ of the target subcircuit using GB based abstraction;
